### 2025-08-14 chapters/system-architecture.tex
revised 3.4 to include cache configurations

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=1.75cm]
\node (start)   [process] {Start: Define Benchmark Set};
\node (config)  [process, below of=start] {Select Hardware Configuration};
\node (native)  [process, below of=config] {Run Benchmarks in Native Mode};
\node (enclave) [process, below of=native] {Run Benchmarks in Enclave Mode};
\node (metrics) [process, below of=enclave] {Collect Performance Metrics};
\node (analyze) [process, below of=metrics] {Compare and Analyze Overheads};
\node (end)     [process, below of=analyze] {Store Logs and Archive Results};

\draw [arrow] (start)   -- (config);
\draw [arrow] (config)  -- (native);
\draw [arrow] (native)  -- (enclave);
\draw [arrow] (enclave) -- (metrics);
\draw [arrow] (metrics) -- (analyze);
\draw [arrow] (analyze) -- (end);
\end{tikzpicture}
\caption{Benchmarking and Data Collection Workflow}
\label{fig:benchmarking-workflow}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    >=latex,
    node distance=1.4cm and 3.5cm,
    lane/.style={
        rectangle,
        draw=black!80,
        thick,
        minimum width=6.5cm,
        minimum height=0.8cm,
        rounded corners,
        align=center,
        text width=6.2cm,
        fill=gray!5
    },
    arrow/.style={->, very thick},
    laneTitle/.style={
        font=\bfseries,
        fill=blue!15,
        rounded corners,
        draw=black!80,
        minimum height=0.8cm
    }
]

% Lane titles
\node[laneTitle, text width=6.5cm] (lane1) {Setup \& Configuration};
\node[laneTitle, right=of lane1]   (lane2) {Execution \& Analysis};

% Setup lane nodes
\node[lane, below=of lane1] (start)   {\textbf{Define benchmark set}};
\node[lane, below=of start] (config)  {\textbf{Select hardware configuration}};

% Execution lane nodes
\node[lane, below=of lane2] (native)  {\textbf{Run benchmarks in native mode}};
\node[lane, below=of native] (enclave) {\textbf{Run benchmarks in enclave mode}};
\node[lane, below=of enclave] (metrics) {\textbf{Collect performance metrics}};
\node[lane, below=of metrics] (analyze) {\textbf{Compare and analyze overheads}};
\node[lane, fill=green!10, below=of analyze] (end) {\textbf{Store logs and archive results}};

% Arrows
\draw[arrow] (start) -- (config);
\draw[arrow] (config.east) -- ++(0.8,0) -- ++(0,-0.7) -- (native.west);
\draw[arrow] (native) -- (enclave);
\draw[arrow] (enclave) -- (metrics);
\draw[arrow] (metrics) -- (analyze);
\draw[arrow] (analyze) -- (end);

\end{tikzpicture}
\caption{Benchmarking and data collection workflow}
\label{fig:benchmarking-swimlane}
\end{figure}

@@
